Altering Backward Pass Gradients improves Convergence

### 2022-09-16 paper.tex
Modifications 4

\begin{table*}[!th]
\ifpreprint\else\vspace*{-5pc}\fi

\section*{Graphical Abstract (Optional)}

\vskip1pc \fbox{
\begin{tabular}{p{.4\textwidth}p{.5\textwidth}} \bf Altering Backward Pass Gradients
improves Convergence  \\
Bishshoy Das, Milton Mondal\\ Brejesh Lall, Shiv Dutt Joshi, Sumantra Dutta Roy \\[1pc]
& In standard neural network training, the gradients in the backward pass are determined
by the forward pass. As a result, the two stages are coupled. This is how most neural
networks are trained currently. However, gradient modification in the backward pass has
seldom been studied in the literature. In this paper we explore decoupled training,
where we alter the gradients in the backward pass. We propose a simple yet powerful
method called PowerGrad Transform, that alters the gradients before the weight update in
the backward pass and significantly enhances the predictive performance of the neural
network. PowerGrad Transform trains the network to arrive at a better optima at
convergence. It is computationally extremely efficient, virtually adding no additional
cost to either memory or compute, but results in improved final accuracies on both the
training and test sets. PowerGrad Transform is easy to integrate into existing training
routines, requiring just a few lines of code. PowerGrad Transform makes it possible for
the network to better fit the training data. With decoupled training, PowerGrad
Transform improves baseline accuracies for ResNet-50 by 0.73\%, for SE-ResNet-50 by
0.66\% and by more than 1.0\% for the non-normalized ResNet-18 network on the ImageNet
classification task.
\end{tabular}
}

\clearpage
\thispagestyle{empty}

\ifpreprint
  \vspace*{-1pc}
\else
%  \vspace*{-6pc}
\fi

@@

where first the gradient $\nabla_{W_D}(L)$ is transformed using the transformation
function `$f$' and then this transformed gradient is propagated through the rest of the
backward graph and all other gradient vectors $\nabla_{W_i}(L)^{*}$ are computed as is.
Because of the early injection of the transformed gradients, all other gradient vectors
that are connected to the transformed gradient through the chain rule, gets subsequently
altered.

>>>>

@@

where first the gradient $\nabla_{W_D}(L)$ is transformed using the transformation
function `$f$' and then this transformed gradient is propagated through the rest of the
backward graph. All other gradient vectors $\nabla_{W_i}(L)^{*}$ are computed as is, but
because of the early injection of the transformed gradient $\nabla_{W_D}(L)$, all other
gradient vectors that are connected to the transformed gradient through the chain rule
($\nabla_{W_i}(L)^{*}$,\ \ i=D-1,\ldots,1), gets subsequently altered.
